Online (Bandit) Policy Selection for EASY-Backfilling

### 2017-04-02 paper/src/paper.tex
paper modif.
fix paper
paper change

\documentclass[sigconf,review]{acmart}
\setcopyright{rightsretained}

@@

@@

\begin{table*}[]
  \centering
  \ra{1.3}
  \caption{Average Cumulative waiting time improvement with respect to EASY-FCFS of fixed policies.}
  \label{tab:full}
  \begin{tabular}{@{}lrrrrrrrrrrr@{}}
    \hline
    Trace        & LCFS & LPF & SPF & LQF & SQF & SEXP & LEXP & LRF & SRF & LAF & SAF \\
    \hline
    KTH-SP2      & LCFS & LPF & SPF & LQF & SQF & SEXP & LEXP & LRF & SRF & LAF & SAF\\
    CTC-SP2      & LCFS & LPF & SPF & LQF & SQF & SEXP & LEXP & LRF & SRF & LAF & SAF\\
    SDSC-SP2     & LCFS & LPF & SPF & LQF & SQF & SEXP & LEXP & LRF & SRF & LAF & SAF\\
    SDSC-BLUE    & LCFS & LPF & SPF & LQF & SQF & SEXP & LEXP & LRF & SRF & LAF & SAF\\
    ANL-Intrepid & LCFS & LPF & SPF & LQF & SQF & SEXP & LEXP & LRF & SRF & LAF & SAF\\
    CEA-Curie    & LCFS & LPF & SPF & LQF & SQF & SEXP & LEXP & LRF & SRF & LAF & SAF\\
    Unilu-Gaia   & LCFS & LPF & SPF & LQF & SQF & SEXP & LEXP & LRF & SRF & LAF & SAF\\
    \hline
  \end{tabular}
\end{table*}

We begin by attracting the attention of the reader to Table~\ref{tab:full},
which reports the average cumulative waiting time performance improvement over
EASY(FCFS,40h) of all the fixed policies defined in ~\ref{subsec:policies}. More
precisely, let us denote the resampled traces of a given workload by $T_k$,
where k is the index of the resampled trace ($1 \le k \le 100$). We also denote
the number of jobs in the resampled trace $T_k$ by $l(T_k)$. We denote by
$\bar{w}(T_k,S)$ the cumulative waiting time obtained by a simulation run for a
strategy $S$:

@@

\begin{figure}[]
  \centering
  \includegraphics[scale=0.6]{figures/full-UniLu-Ga.pdf}
  \caption{Evolution of the average cumulative waiting time improvement
    compared to EASY-FCFS of the policies $P_i$ for $i = 1 \ldots 10$ on the
    UniLu-Gaia trace. The average is obtained by resampling the original trace
    100 times. The dashed lines represent the 10th and 90th percentiles of the
  values across this resampling.}
  \label{fig:all}
\end{figure}

Figure~\ref{fig:all} reports the evolution of this quantity for the UniLu-Gaia
trace, which means that it shows how the average improvement in cumulative
waiting time evolves as a function of time. In other words, this is the average
curve obtained if one were to plot the cumulative sum of job waiting times for
every resampled trace, incrementing the sum when a job finishes. Accordingly,
the final values attained by every curve correspond exactly to the values
reported in Table~\ref{tab:full}. The dashed values represent the 10th and 90th
percentile of the values.

Observe that \textcolor{orange}{TODO}

>>>>

\documentclass[sigconf,review,anonymous]{acmart}
\setcopyright{rightsretained}

@@

\acmConference[SC’15]{Supercomputing}{May 29 -- June 2}{Orlando, FL, USA}

@@

\begin{table*}[]
  \centering
  \ra{1.3}
  \caption{Average total waiting time diminution of fixed policies with respect to EASY(FCFS).}

  %DELTA WEEK

  \label{tab:full}
  \begin{tabular}{@{}lrrrrrrrrrrr@{}}
    \hline
    Trace        & LCFS  & LPF            & SPF   & LQF            & SQF   & SEXP  & LEXP           & LRF            & SRF   & LAF          & SAF   \\
    \hline
    ANL-Intrepid & -25\% & -9\%           & -3\%  & \textbf{-28\%} & -2\%  & -21\% & -24\%          & -21\%          & -10\% & -19\%        & +5\%  \\
    KTH-SP2      & -13\% & \textbf{-16\%} & +5\%  & \textbf{-16\%} & +3\%  & -8\%  & -15\%          & -8\%           & -13\% & -12\%        & +15\% \\
    CTC-SP2      & -40\% & -19\%          & -14\% & \textbf{-47\%} & +15\% & -36\% & -19\%          & -38\%          & -12\% & -44\%        & +22\% \\
    SDSC-SP2     & -8\%  & \textbf{-15\%} & +4\%  & -8\%           & +4\%  & -3\%  & \textbf{-15\%} & -3\%           & -10\% & -11\%        & +18\% \\
    SDSC-BLUE    & -26\% & -29\%          & 0\%   & -29\%          & +17\% & -17\% & -26\%          & -15\%          & -15\% & \textbf{-32\%} & +23\% \\
    CEA-Curie    & -46\% & -23\%          & -45\% & \textbf{-57\%} & -19\% & -51\% & -23\%          & \textbf{-57\%} & -24\% & -40\%        & -17\% \\
    Unilu-Gaia   & -58\% & -33\%          & -10\% & \textbf{-62\%} & +16\% & -49\% & -27\%          & -56\%          & -16\% & -62\%        & +20\% \\
    \hline
  \end{tabular}
\end{table*}

We begin by attracting the attention of the reader to Table~\ref{tab:full},
which reports the average total waiting time performance improvement over
EASY(FCFS,40h) of all the fixed policies defined in ~\ref{subsec:policies}. More
precisely, let us denote the resampled traces of a given workload by $T_k$,
where k is the index of the resampled trace ($1 \le k \le 100$). We also denote
the number of jobs in the resampled trace $T_k$ by $l(T_k)$. We denote by
$\bar{w}(T_k,S)$ the cumulative waiting time obtained by a simulation run for a
strategy $S$:

@@

The best values are outlined in bold in the table. These values give the best
attainable performance in the search set defined in~\ref{subsec:policies}.
Note that there seems to be some regularity; the SAF policy is remarkably
inefficient for instance, and the LQF policy works very well. However, note
that there are traces for which LQF is not optimal. Moreover, these
are~\textit{a-posteriori} results, which means that we only know post-factum
that this policy would have been better. In the present work, we are
studying adaptive policies that obtain a good performance on any given system
by selecting one of these policies.

\begin{figure}[]
  \centering
  \includegraphics[scale=0.6]{figures/full-ANL-Intr.pdf}
  \caption{Evolution of the average cumulative waiting time improvement
    compared to EASY-FCFS of the policies $P_i$ for $i = 1 \ldots 10$ on the
    UniLu-Gaia trace. The average is obtained by resampling the original trace
    100 times. The dashed lines represent the 10th and 90th percentiles of the
  values across this resampling.}
  \label{fig:all}
\end{figure}

Figure~\ref{fig:all} reports the evolution of the average cumulative waiting
time for the UniLu-Gaia tis quantityrace, which means that it shows how the
average improvement in cumulative waiting time evolves as a function of time.
In other words, this is the average curve obtained if one were to plot the
cumulative sum of job waiting times for every resampled trace, incrementing the
sum when a job finishes. Accordingly, the final values attained by every curve
correspond exactly to the values reported in Table~\ref{tab:full}. The dashed
values represent the 10th and 90th percentile of the values.

Observe that while the 10th and 90th percentiles of the improvement with
respect to EASY-FCFS are large, the values are still contained enough to make
definite statements about how these policies compare to the FCFS baseline.
This figure does not report the variability of the policies against one another,
and does not allow to compare them beyong comparing their average performance.
However, the fact that the band of percentiles are roughly of the size of half
the best attainable improvement was our original motivation for this work, as
one can expect to be able to distinguish between these policies in an
online manner.
